---
title: "Brickman"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Convenience tools for accessing Brickman Gulf of `Maine 2050` model outputs.

> Cf: [Brickman D, Alexander MA, Pershing A, Scott JD, Wang Z. Projections of physical conditions in the Gulf of Maine in 2050. Elem Sci Anth. 2021 May 6;9(1):00055.](https://online.ucpress.edu/elementa/article/9/1/00055/116900/Projections-of-physical-conditions-in-the-Gulf-of)

Contents:

 + PRESENT CLIMATE
 
 + RCP45
   - year 2055
   - year 2075
   
 + RCP85
   - year 2055
   - year 2075
   
Variables:

 + Bathy_depth, land_mask
 + Annual means: SST, MLD, SSS, Sbtm, Tbtm, U, V, Xbtm
 + Monthly means: SST, MLD, SSS, Sbtm, Tbtm, U, V, Xbtm


### Requirements

 + [R v4.1+](https://R-project.org)
 + [rlang](https://CRAN.R-project.org/package=rlang)
 + [dplyr](https://CRAN.R-project.org/package=dplyr)
 + [ncdf4](https://CRAN.R-project.org/package=ncdf4)
 + [stars](https://CRAN.R-project.org/package=stars)
 + [sf](https://CRAN.R-project.org/package=sf)

### Installation

```
remotes::install_github("BigelowLab/brickman")
```

### Usage

```{r, message = FALSE, warning = FALSE}
suppressPackageStartupMessages({
    library(stars)
    library(brickman)
  })

x <- brickman::read_brickman(scenario ='RCP85', year = 2055, vars = 'SST', interval = "mon")
plot(x)
```
